The competing effects of the immune system and EMT on epithelial cancers

### 2019-03-25 Paper/Paper.tex
Removed old comments and added refs

@@

The effects of the immune system on a tumor can be broadly summarized into two modules. The cytotoxic branch of the immune system (such as natural killer (NK) cells and cytotoxic T cells (CTLs)) seek out and lyse tumor cells. The regulatory branch of the immune system (T regulatory cells (Tregs) and other factors), inhibits the effective functioning of the cytotoxic branch. [REF]

@@

%There are also other structural changes that take place in mesenchymal cells that could contribute to this refractory nature towards immune clearance.
%Regardless, the evidence currently demonstrates a ``slipperiness'' of mesenchymal cells in regards to immune lysing.

@@

While many qualities are associated with being stem-like, we choose to focus on a reduced proliferation rate. \tcr{Ref}

@@

% This paragraph needs to find a home in this section somewhere

@@

\subsection{Tissue Cells}\label{TissueCells}
The tissue cells at all times have associated with them two important quantities: which combination of mutations they carry and an EMT score.
The model has three pathways that have the potential to mutate over the course of a simulation.
There is a proliferation pathway that when mutated increases the probability of the cell proliferating.
There is an apoptosis pathway that when mutated decreases the probability of the cell undergoing apoptosis.
There is an immune evasion pathway that when mutated decreases the probability that an immune cell can effectively clear the mutated cell.
% It might be nice to have a table to summarize this information?
The EMT score will be exposited in Section \ref{EMT}. % make sure this is really the best decision

%Add differential equations? % Should this be done here or where I have it later?

@@

\begin{equation}\tag{2.3}
\rho_{\text{NK}} =\delta_{\text{MUT}} \frac{N_{\text{NK}}}{N_C/K_{1}+N_{\text{NK}}}  \frac{E_{\text{NK}}}{1+N_{\text{Treg}}/K_2} (1-\delta_{\text{IE}}\Delta_{\text{IE}})(1-\zeta \Delta_{\text{MIE}})
\end{equation}
% Should I worry about the order in which these appear? Rearranging would make the formula look better, but the order I have introduced them makes the most sense.
% Also, any thoughts on NK, CTL, Treg not being italicized? While other capital letters are?

@@

%%%% Which of these two paragraphs is better? Currently the intro does not mention APCs and I don't think I need to go into that, especially when APC_k = \tilde{M}_k
For CTLs and Tregs, they rely on mutant cells being cleared before they can be activated.
Let $N_{\text{MUT}}^*(k)$ represent the number of mutant cells cleared by the immune system during cell cycle $k$.
In addition, Treg recruitment is upregulated by TGF-$\beta$, which will be incorporated via a Hill function with EC50 term $K_4$.
We choose the following differential equations to govern the CTL and Treg populations:

@@

\begin{figure}
\center
{\includegraphics[width=0.8\textwidth]{Figure1/Figure1.pdf}}
\caption{A. Schematic depiction of the model with blue/red denoting non-mutated/mutated cells in the agent-based model. In each cycle, the fate of a cell is regulated by the EMT state of the cell and by any pathway mutations harbored. Inset shows major processes of immune system regulation on the tissue cells. The parameters used in this model can be found in the Supplementary material. Unless otherwise stated, parameter values are assumed to be those found in the Supplement. \tcr{Thoughts on the wording here? Once I have the table, I will use the name of that table.}
B. Example simulation of the dynamics of a one patient; warmup period ends at the vertical dashed line.
The inflammation cycling scheme is graphically represented above the patient dynamics.
C. Example survival curve for one cohort of patients with basal parameter values.
%A Should I list out all parameter values? A subset? Or refer to supplement for base parameter values?
D. Global sensitivity analysis of model parameters using the Morris one-step-at-a-time method.}
\label{fig:ModelIntro}
\end{figure}

We begin by investigating general features of the model to establish baseline conditions and to assess the impact of various model components on the key measured outcomes: the probability of cancer, and the Time to Cancer. 
Within the cell cycle, cell fate is determined via a set of rules that are influenced by EMT and immune interactions (Fig. \ref{fig:ModelIntro}A). For example, if a cell undergoes EMT, the probability that it will proliferate is reduced; if a cell gains a mutation in the apoptosis pathway, the probability that it undergoes apoptosis is greatly reduced. The different means by which the immune system acts on tissue cells are also shown (\ref{fig:ModelIntro}A Inset). NK cells and CTLs attempt to clear mutated tissue cells, and deactivate upon successfully carrying out their cytotoxic function. T regulatory cells (Tregs) inhibit cytotoxic activity. Tregs also release TGF-$\beta$ which promotes the recruitment of Tregs, as well as increasing the rate of EMT.
\par
The inflammation cycling scheme for a typical {\it in silico} patient consists of alternating high and low regimes (Fig. \ref{fig:ModelIntro}B); the inflammation schemes modeled will be discussed in detail in the next section. For this patient, after the warmup period, cell mutations are observed at a rate low enough that they are cleared by cytotoxic cells before being able to establish a tumor. However, after approximately 1000 cell cycles (750 days), one mutated cell exhibits clonal growth, and a tumor is established. At this point, large numbers of cells from the adaptive immune system (CTLs and Tregs) are being heavily recruited, and a peak in TGF-$\beta$ expression is observed. The number of mesenchymal cells increases initially with increasing TGF-$\beta$, but decreases after the clone takes over the tissue. This shifts back towards an epithelial tissue phenotype occurs even though the expression of TGF-$\beta$ remains high.
After 841 cell cycles, the proportion of mutated cells reaches 50\%: this is modeled as the threshold defining tumorigenesis. Thus this patient has a Time to Cancer of 841 cell cycles, or 631 days. 
After cancer incidence, the number of mutated cells continues to grow rapidly and soon makes up 100\% of the cell population. A peak in mesenchymal phenotypes is observed following cancer incidence, before most transition back to an epithelial state.
\par 
Considering the immune system dynamics, we see that the NK population is approximately constant, while the adaptive populations (CTL and Treg cells) grow quickly and dwarf NK cells in number following the accumulation of oncogenic mutations.
%Note: NK cells also lymphocytes! 
The adaptive immune populations also appear to exhibit oscillatory behavior, however note that this is not due to intrinsic dynamics but rather due to the inflammation scheme that the patient is undergoing: alternating between 30 cell cycles of high inflammation and 60 cell cycles of low inflammation. Within each of these periods, adaptive immune populations increase or decrease rapidly in accordance with the inflammation state.
\par 
The {\em in silico} patient described here is given for the purpose of illustrating features of the model. Given the multiple sources of noise in the model, in order to quantify patient dynamics and cancer-free survival rates, below we will simulate large cohorts of patients. In Fig. \ref{fig:ModelIntro}C we simulate the survival curve for a cohort of $500$ patients: we see that all the patients survive for approximately 100 cell cycles (75 days). Subsequently, in the approximate range of $T= [100,300]$, the cancer onset rate is roughly constant, and after $600$ cell cycles, no patients remain cancer free.

\subsection{Identification of key regulatory parameters via Morris global sensitivity analysis}\label{SensAnalysis}
To assess the sensitivity of the model parameters and thus identify those that are most important in determining cancer-free survival times, we applied Morris one-step-at-a-time (OAT) sensitivity analysis (see Methods) to the model.
The results of Morris OAT on the 31 model parameters are shown in \ref{fig:MOAT}: a subset of parameters demonstrate much higher levels of sensitivity than others.
The two most influential according to this analysis are the death rate and the recruitment rate of Treg cells, this is most likely due to the dual roles Treg cells play in both suppressing the cytotoxic effects of other immune cells and secreting TGF-$\beta$, which drives EMT.
This ties Treg cells to all three components of the model.
Since we seek to separate the effects of different model components, we do not choose the parameters influencing Treg cells for detailed analysis below.
\par
%% We need to discuss parameter names. Maybe replace 'low' with 'base' and 'up' with 'gain' ?
Many parameters in the model change depending on the inflammation state.
For the sake of a naming convention, any parameter which includes ``low'' in the name represents the parameter value when inflammation is low.
For when the inflammation is high, these ``low'' parameters get scaled by parameters which include ``up'' in the name.
The ILD and IHD parameters determine the duration of low and high inflammation, respectively.
A cell with mutated pathways will be affected by the $\Delta_A$, $\Delta_P$, and $\Delta_{\text{IE}}$ parameters, depending on whether the apoptosis, proliferation, or immune evasion pathways are mutated.
The mesenchymal cells are influenced by the MGA and MIE parameters.
Finally, $\sigma$, $k_\text{EMT}$, $\tau_\text{max}$, and $K_3$ all control how cells transition between the epithelial and mesenchymal states.

Since one goal of our analysis is to assess the specific effects of EMT on immune-cancer dynamics, the parameters MIE and MGA are of particular interest.
In addition, inflammation parameters dictating the cycling scheme are important to study\tcr{REF}: we find that there are also high sensitivities in this model to these parameters.
In terms of Treg cells, their secretion of TGF-$\beta$ is highly significant and we will also study it further.

@@

We explored the effects of varying the inflammation state of the patient on cancer-free survival, to investigate competing interactions within the TME and their effect on EMT. Patient cohorts were simulated under different inflammation regimes: permanently low inflammation; permanently high inflammation; or variable inflammation. For patients drawn from cohorts in a permanently high inflammatory state, the relationship between mesenchymal parameters and the Time to Cancer is monotonic, i.e. increasing either the rate of mesenchymal immune evasion (MIE) (Fig. \ref{fig:VaryINFL_and_MesPars}A-B) or of mesenchymal growth arrest (MGA)  (Fig. \ref{fig:VaryINFL_and_MesPars}C-D) decreases the Time to Cancer.
However, under regimes with either temporary or permanent periods of low inflammation, different relationships emerge: a local maximum for the Time to Cancer is found with respect to the relative mesenchymal growth rate (MGA $= 0.3$). This is seen both for intermittent or low inflammation (Fig. \ref{fig:VaryINFL_and_MesPars}D). 
\par
These striking differences in the mean Time to Cancer -- extended by up to one year by fine-grained optimization of mesenchymal growth arrest -- have clear therapeutic implications. 
%What this indicates is that if the growth arrest of mesenchymal cells can be controlled, then they could be manipulated in such a way as to increase the Time to Cancer.
%For patients presenting with chronically high inflammatory state, anti-inflammatories could be administered which would create the periods of low inflammation our model predicts as necessary for seeing these changes.
Our model predicts that reducing the inflammatory state of the TME in three weeks out of every nine would be provide means to prolong cancer-free survival in combination with mesenchymal cell therapies to make the control of mesenchymal proliferation an effective anti-cancer strategy.
\par
In contrast, when MIE is varied for different inflammation cycling schemes, regardless of the cycling scheme, increasing the MIE leads to decreases in the Time to Cancer (worse survival probabilities), although in the case where the inflammatory state is permanently high, MIE has little effect on the Time to Cancer. Thus under any inflammation regime with periods of low inflammation, any reductions in the rate of mesenchymal immune evasion will lead to improved patient outcomes.

@@

% \subsection{Heat Map of MIE vs MGA}
\subsection{Analysis of TCGA data in comparison with model predictions suggests that mesenchymal phenotypes reduce cancer-free survival probability}\label{tcga}

@@

%% AM: no need to separate this I think - combine conclusions into the discussion section. 
%\section{Conclusion}\label{Conclusion}
The interactions of the immune system and cancer remain a promising avenue of research.
Including more diverse aspects of the TME and the tumor itself make the challenge that much harder but also that much more promising.
As we begin to understand how processes such as EMT factor in to these complex interactions, we can begin to respond clinically to better improve patient outcomes.
Here, we saw {\it in silico} evidence of an optimal value for a property of mesenchymal cells that would maximize Time to Cancer.
There is still much work to be done further isolating this effect in computer simulations and further verifying this effect and exploring further ways EMT can influence tumor progression.
This model explored much more than mesenchymal growth arrest, so a simpler model could make this point clearer.
On the other hand, models which incorporate more distinctions between epithelial and mesenchymal cells could give better clarity on the relative importance of these and reveal a fuller picture about how a mesenchymal subpopulation affects cancer outcomes.

%A Adam, do you know of any?
The authors are not aware of current treatments that specifically target mesenchymal growth arrest, influencing it in one direction or another.
%
Based on these results, this could prove to be a promising direction for research, in particular for cancers in which it is known that mesenchymal cells are present and active within the tumor.
The greatest challenge in translating the information here to the clinic, apart from creating the drugs, would be discovering the ideal growth rate for mesenchymal cells within each patient and how other patient-specific data will influence this result.

Progress in cancer treatment has always proven attainable even despite great challenges, for which the complexity of the disease is often responsible. As we move forwards, it is these very complexities that we will be able to better exploit to eradicate or control the disease.

>>>>

%%%% Possible additional refs:
% Diefenbach 2001
% They show that when tumor cells express a particular marker, then the immune system gains considerable potency and clears the tumor. Furthermore, immunization via tumor cells expressing these ligands creates a host immunity to subsequent tumors even if these tumors lack the ligand.

% Carretero 2015
% As eosinophils can better carry out their recruitment function of CD8+ T cells, tumor rejection by the immune system is more readily accomplished.

% Ju 2016
% A cancer vaccine was demonstrated to be effective in reducing colorectal cancer incidence in mice. In addition, efficacy of CTLs was shown to be increased.

@@

The effects of the immune system on a tumor can be broadly summarized into two modules. The cytotoxic branch of the immune system (such as natural killer (NK) cells and cytotoxic T cells (CTLs) seek out and lyse tumor cells.
Upon carrying out their effector functions, these cytotoxic cells lose efficacy or deactivate entirely\tcr{[REF]}.
The regulatory branch of the immune system (T regulatory cells (Tregs) and other factors), inhibits the effective functioning of the cytotoxic branch\cite{ruffell2010lymphocytes}.

@@

@@

While many qualities are associated with being stem-like, we choose to focus on a reduced proliferation rate\cite{woods2014effects}.

@@

@@

\subsection{Tissue Cells}\label{TissueCells}
The tissue cells at all times have associated with them two important quantities: which combination of mutations they carry and an EMT score.
The model has three pathways that have the potential to mutate over the course of a simulation.
There is a proliferation pathway that when mutated increases the probability of the cell proliferating.
There is an apoptosis pathway that when mutated decreases the probability of the cell undergoing apoptosis.
There is an immune evasion pathway that when mutated decreases the probability that an immune cell can effectively clear the mutated cell.
The EMT score will be exposited in Section \ref{EMT}.

@@

\begin{equation}\tag{2.3}
\rho_{\text{NK}} =\delta_{\text{MUT}} \frac{N_{\text{NK}}}{N_C/K_{1}+N_{\text{NK}}}  \frac{E_{\text{NK}}}{1+N_{\text{Treg}}/K_2} (1-\delta_{\text{IE}}\Delta_{\text{IE}})(1-\zeta \Delta_{\text{MIE}})
\end{equation}

@@

For CTLs and Tregs, they rely on mutant cells being cleared before they can be activated.
Let $N_{\text{MUT}}^*(k)$ represent the number of mutant cells cleared by the immune system during cell cycle $k$.
In addition, Treg recruitment is upregulated by TGF-$\beta$, which will be incorporated via a Hill function with EC50 term $K_4$.
We choose the following differential equations to govern the CTL and Treg populations:

@@

\begin{figure}
\center
{\includegraphics[width=0.8\textwidth]{Figure1/Figure1.pdf}}
\caption{A. Schematic depiction of the model with blue/red denoting non-mutated/mutated cells in the agent-based model. In each cycle, the fate of a cell is regulated by the EMT state of the cell and by any pathway mutations harbored. Inset shows major processes of immune system regulation on the tissue cells. The parameters used in this model can be found in the Supplementary material. Unless otherwise stated, parameter values are assumed to be those found in the Supplement. \tcr{Thoughts on the wording here? Once I have the table, I will use the name of that table.}
B. Example simulation of the dynamics of a one patient; warmup period ends at the vertical dashed line.
The inflammation cycling scheme is graphically represented above the patient dynamics.
C. Example survival curve for one cohort of patients with basal parameter values.
D. Global sensitivity analysis of model parameters using the Morris one-step-at-a-time method.}
\label{fig:ModelIntro}
\end{figure}

We begin by investigating general features of the model to establish baseline conditions and to assess the impact of various model components on the key measured outcomes: the probability of cancer, and the Time to Cancer. 
Within the cell cycle, cell fate is determined via a set of rules that are influenced by EMT and immune interactions (Fig. \ref{fig:ModelIntro}A). For example, if a cell undergoes EMT, the probability that it will proliferate is reduced; if a cell gains a mutation in the apoptosis pathway, the probability that it undergoes apoptosis is greatly reduced. The different means by which the immune system acts on tissue cells are also shown (\ref{fig:ModelIntro}A Inset). NK cells and CTLs attempt to clear mutated tissue cells, and deactivate upon successfully carrying out their cytotoxic function. T regulatory cells (Tregs) inhibit cytotoxic activity. Tregs also release TGF-$\beta$ which promotes the recruitment of Tregs, as well as increasing the rate of EMT.
\par
The inflammation cycling scheme for a typical {\it in silico} patient consists of alternating high and low regimes (Fig. \ref{fig:ModelIntro}B); the inflammation schemes modeled will be discussed in detail in the next section. For this patient, after the warmup period, cell mutations are observed at a rate low enough that they are cleared by cytotoxic cells before being able to establish a tumor. However, after approximately 1000 cell cycles (750 days), one mutated cell exhibits clonal growth, and a tumor is established. At this point, large numbers of cells from the adaptive immune system (CTLs and Tregs) are being heavily recruited, and a peak in TGF-$\beta$ expression is observed. The number of mesenchymal cells increases initially with increasing TGF-$\beta$, but decreases after the clone takes over the tissue. This shifts back towards an epithelial tissue phenotype occurs even though the expression of TGF-$\beta$ remains high.
After 841 cell cycles, the proportion of mutated cells reaches 50\%: this is modeled as the threshold defining tumorigenesis. Thus this patient has a Time to Cancer of 841 cell cycles, or 631 days. 
After cancer incidence, the number of mutated cells continues to grow rapidly and soon makes up 100\% of the cell population. A peak in mesenchymal phenotypes is observed following cancer incidence, before most transition back to an epithelial state.
\par 
Considering the immune system dynamics, we see that the NK population is approximately constant, while the adaptive populations (CTL and Treg cells) grow quickly and dwarf NK cells in number following the accumulation of oncogenic mutations.
The adaptive immune populations also appear to exhibit oscillatory behavior, however note that this is not due to intrinsic dynamics but rather due to the inflammation scheme that the patient is undergoing: alternating between 30 cell cycles of high inflammation and 60 cell cycles of low inflammation. Within each of these periods, adaptive immune populations increase or decrease rapidly in accordance with the inflammation state.
\par 
The {\em in silico} patient described here is given for the purpose of illustrating features of the model. Given the multiple sources of noise in the model, in order to quantify patient dynamics and cancer-free survival rates, below we will simulate large cohorts of patients. In Fig. \ref{fig:ModelIntro}C we simulate the survival curve for a cohort of $500$ patients: we see that all the patients survive for approximately 100 cell cycles (75 days). Subsequently, in the approximate range of $T= [100,300]$, the cancer onset rate is roughly constant, and after $600$ cell cycles, no patients remain cancer free.

\subsection{Identification of key regulatory parameters via Morris global sensitivity analysis}\label{SensAnalysis}
To assess the sensitivity of the model parameters and thus identify those that are most important in determining cancer-free survival times, we applied Morris one-step-at-a-time (OAT) sensitivity analysis (see Methods) to the model.
The results of Morris OAT on the 31 model parameters are shown in \ref{fig:MOAT}: a subset of parameters demonstrate much higher levels of sensitivity than others.
The two most influential according to this analysis are the death rate and the recruitment rate of Treg cells, this is most likely due to the dual roles Treg cells play in both suppressing the cytotoxic effects of other immune cells and secreting TGF-$\beta$, which drives EMT.
This ties Treg cells to all three components of the model.
Since we seek to separate the effects of different model components, we do not choose the parameters influencing Treg cells for detailed analysis below.
\par
Many parameters in the model change depending on the inflammation state.
For the sake of a naming convention, any parameter which includes ``low'' in the name represents the parameter value when inflammation is low.
For when the inflammation is high, these ``low'' parameters get scaled by parameters which include ``up'' in the name.
The ILD and IHD parameters determine the duration of low and high inflammation, respectively.
A cell with mutated pathways will be affected by the $\Delta_A$, $\Delta_P$, and $\Delta_{\text{IE}}$ parameters, depending on whether the apoptosis, proliferation, or immune evasion pathways are mutated.
The mesenchymal cells are influenced by the MGA and MIE parameters.
Finally, $\sigma$, $k_\text{EMT}$, $\tau_\text{max}$, and $K_3$ all control how cells transition between the epithelial and mesenchymal states.

Since one goal of our analysis is to assess the specific effects of EMT on immune-cancer dynamics, the parameters MIE and MGA are of particular interest.
In addition, inflammation parameters dictating the cycling scheme are of interest because they are both highly influential on Time to Cancer and capable of being targeted by therapeutic treatments.
In terms of Treg cells, their secretion of TGF-$\beta$ is highly significant and we will also study it further.

@@

We explored the effects of varying the inflammation state of the patient on cancer-free survival, to investigate competing interactions within the TME and their effect on EMT. Patient cohorts were simulated under different inflammation regimes: permanently low inflammation; permanently high inflammation; or variable inflammation. For patients drawn from cohorts in a permanently high inflammatory state, the relationship between mesenchymal parameters and the Time to Cancer is monotonic, i.e. increasing either the rate of mesenchymal immune evasion (MIE) (Fig. \ref{fig:VaryINFL_and_MesPars}A-B) or of mesenchymal growth arrest (MGA)  (Fig. \ref{fig:VaryINFL_and_MesPars}C-D) decreases the Time to Cancer.
However, under regimes with either temporary or permanent periods of low inflammation, different relationships emerge: a local maximum for the Time to Cancer is found with respect to the relative mesenchymal growth rate (MGA $= 0.3$). This is seen both for intermittent or low inflammation (Fig. \ref{fig:VaryINFL_and_MesPars}D). 
\par
These striking differences in the mean Time to Cancer -- extended by up to one year by fine-grained optimization of mesenchymal growth arrest -- have clear therapeutic implications. 
Our model predicts that reducing the inflammatory state of the TME in three weeks out of every nine would be provide means to prolong cancer-free survival in combination with mesenchymal cell therapies to make the control of mesenchymal proliferation an effective anti-cancer strategy.
\par
In contrast, when MIE is varied for different inflammation cycling schemes, regardless of the cycling scheme, increasing the MIE leads to decreases in the Time to Cancer (worse survival probabilities), although in the case where the inflammatory state is permanently high, MIE has little effect on the Time to Cancer. Thus under any inflammation regime with periods of low inflammation, any reductions in the rate of mesenchymal immune evasion will lead to improved patient outcomes.

@@

\subsection{Analysis of TCGA data in comparison with model predictions suggests that mesenchymal phenotypes reduce cancer-free survival probability}\label{tcga}

@@

%% AM: no need to separate this I think - combine conclusions into the discussion section. 
%\section{Conclusion}\label{Conclusion}
The interactions of the immune system and cancer remain a promising avenue of research.
Including more diverse aspects of the TME and the tumor itself make the challenge that much harder but also that much more promising.
As we begin to understand how processes such as EMT factor in to these complex interactions, we can begin to respond clinically to better improve patient outcomes.
Here, we saw {\it in silico} evidence of an optimal value for a property of mesenchymal cells that would maximize Time to Cancer.
There is still much work to be done further isolating this effect in computer simulations and further verifying this effect and exploring further ways EMT can influence tumor progression.
This model explored much more than mesenchymal growth arrest, so a simpler model could make this point clearer.
On the other hand, models which incorporate more distinctions between epithelial and mesenchymal cells could give better clarity on the relative importance of these and reveal a fuller picture about how a mesenchymal subpopulation affects cancer outcomes.
%A Adam, do you know of any?
The authors are not aware of current treatments that specifically target mesenchymal growth arrest, influencing it in one direction or another.
%
Based on these results, this could prove to be a promising direction for research, in particular for cancers in which it is known that mesenchymal cells are present and active within the tumor.
The greatest challenge in translating the information here to the clinic, apart from creating the drugs, would be discovering the ideal growth rate for mesenchymal cells within each patient and how other patient-specific data will influence this result.
\par
Also, since the inflammatory state of the TME played such a large role in our simulations, making this a more robust facet of the model by allowing the tumor and immune system to influence the inflammatory state could give the model higher fidelity.
One intriguing aspect could be the anti-inflammatory function of Tregs as they seek to restore homeostasis.
\par
A final future direction would be continuing to explore the heterogeneity of the tumor and how this helps the tumor evade the immune system and grow into a malignancy. 
As we understand more and more about the diversity within the TME, additional models will be instrumental in determining the scope of these implications and the possible ways to address them.
\par
Progress in cancer treatment has always proven attainable even despite great challenges, for which the complexity of the disease is often responsible. As we move forwards, it is these very complexities that we will be able to better exploit to eradicate or control the disease.
